00-Data-Preprocessing

### 2021-05-21 R0-Density-Reanalysis/R0-Density-Reanalysis.Rmd
Revised data package to include boundaries of urbanized areas

Thanks to the availability of code and data, it was possible to verify the results reported by SWN. As noted earlier, though, an experienced spatial modeller would have asked themselves about the implications of the spatial sampling procedure used by SWN. The decision to use a sample of counties with reliable basic reproductive numbers, although seemingly sensible, results in a non-random sampling scheme. Turning our attention back to Figure \ref{fig:R0-map}, we see that many counties without reliable values of $R_0$ are in more rural, less dense parts of the United States. The fact that $R_0$ could not be accurately computed in those counties does not mean that there was no transmission of the virus: it simply means that we do not know with precision whether that was the case. The low number of cases may be related to low population and/or low population density. This is intriguing, to say the least: by excluding cases in a non-random way such as this, we are in effect _truncating_ the sample.

>>>>

Thanks to the availability of code and data, it was possible to verify the results reported by SWN. As noted earlier, though, an experienced spatial modeller would have asked themselves about the implications of the spatial sampling procedure used by SWN. The decision to use a sample of counties with reliable basic reproductive numbers, although seemingly sensible, results in a non-random spatial sampling scheme. Turning our attention back to Figure \ref{fig:R0-map}, we form the impression that many counties without reliable values of $R_0$ are in more rural, less dense parts of the United States: this is . The fact that $R_0$ could not be accurately computed in those counties does not mean that there was no transmission of the virus: it simply means that we do not know with precision whether that was the case. The low number of cases may be related to low population and/or low population density. This is intriguing, to say the least: by excluding cases in a non-random way such as this, we are in effect _truncating_ the sample.

### 2021-05-21 r0density/raw-data-processing/00-Data-Preprocessing.Rmd
Revised data package to include boundaries of urbanized areas

@@

Save data table:
```{r}
save(county_geo, file = "county_geo.RData", compress = "xz")
save(state_geo, file = "state_geo.RData", compress = "xz")
```

>>>>

Retrieve metropolitan/micropolitan boundaries for plotting:
```{r}
urban_geo <- get_acs(geography = "urban area", 
                            variables = "B01003_001", # Total population
                            year = 2019, 
                            geometry = TRUE, 
                            keep_geo_vars = TRUE) %>%
  rename(population = estimate) %>%
  select(-c(variable, moe))
```

@@

Prepare urban boundaries for saving:
```{r}
# Get state number code and two letter code from state table:
urban_geo <- urban_geo %>%
  st_join(state_geo %>%
            select(STATE, state))
```

Save data table:
```{r}
save(county_geo, file = "county_geo.RData", compress = "xz")
save(urban_geo, file = "urban_geo.RData", compress = "xz")
save(state_geo, file = "state_geo.RData", compress = "xz")
```
